### 2019-06-05 2-Chapters/2-Chapter/chapter2.tex
Je vais lancer les simulations avant d'aller au foot

>>>>

\subsection{A first numerical experiment on the example Bernoulli problem}
\label{sub:2:shortNumericalExperiments}

We finish this Section~\ref{sec:2:famousMABalgorithms} by illustrating the performance of different algorithms, on the small MAB problem used in the online demonstration shown above (see Figures~\ref{fig:2:example_of_a_5_arm_bandit_problem} and \ref{fig:2:example_of_a_5_arm_bandit_problem__step100}).
We consider $K=5$ arms following Bernoulli distributions, of means $\mu_1=0.6,\mu_2=0.2,\mu_3=0.55,\mu_4=0.7,\mu_5=0.5$ (unknown to the algorithms), and first an horizon $T=100$ (like in the online demo) then a large value of $T=10000$.
The best arm is $\mu_4$ and the smallest gap is $\Delta = 0.1$, thus a lower-bound on the gaps is taken as $d=\Delta$.
% (used to tune the two algorithms from Section~\ref{sub:2:naiveSimpleStrategies}).

The different algorithms being compared are the following, in the order they were presented above:
%
first we include the pure-exploration and
pure-exploitation algorithms,
then the $\varepsilon$-greedy (with $\varepsilon_t=\varepsilon_0/t$ and $\varepsilon_0=6K/d^2=3000$) and
Explore-then-Commit (with $T_0=K4/d^2 \log(d^2T/4)=2000\log(T/400)$) algorithms
from Section~\ref{sub:2:naiveSimpleStrategies}, which both uses a tuning based on a prior knowledge of $\Delta$ (that gives large values of $\varepsilon_0$ and $T_0$ yielding linear regret for small horizon).
%
We then include efficient algorithms, that do not need prior knowledge of the $T$ (they are anytime) nor $\Delta$ (their are robust and efficient on unknown problems):
$\UCB_1$ (with $\alpha=1$),
\klUCB{} (with Bernoulli $\kl = \KL_{B}$),
and Thompson sampling (with Beta posteriors and flat uniform priors).
%

We first give in Table~\ref{table:2:oneShotResult} the cumulated rewards as well as the regret of the different algorithms, \emph{for one simulation}.
Then in Table~\ref{table:2:meanResults} we show the results of the average on $N=1000$ independent runs.

\begin{table}[ht]
    \begin{small}  % WARNING
        \centering
        \begin{tabular}{c|cc|cc}
        \textbf{Algorithms} $\;$ \textbackslash $\;$ Horizon & Reward & Regret $T=100$ & Reward & Regret $T=10000$ \\
            \hline
            Pure exploration
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Pure exploitation
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
            $\varepsilon$-greedy
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Explore-then-Commit
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
            $\UCB_1$
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \klUCB{}
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Thompson sampling
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
        \end{tabular}
        \caption{Cumulated rewards and regret, for horizons $T=100$ and $T=10000$, \emph{for only one run of the simulation}, for different algorithms.}
        \label{table:2:oneShotResult}
    \end{small}  % WARNING
\end{table}

\TODOL{Lancer les simulations !}

\begin{table}[ht]
    \begin{small}  % WARNING
        \centering
        \begin{tabular}{c|cc|cc}
        \textbf{Algorithms} $\;$ \textbackslash $\;$ Horizon & Reward & Regret $T=100$ & Reward & Regret $T=10000$ \\
            \hline
            Pure exploration
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Pure exploitation
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
            $\varepsilon$-greedy
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Explore-then-Commit
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
            $\UCB_1$
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \klUCB{}
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            Thompson sampling
                & $XXX$ & $XXX$
                & $XXX$ & $XXX$ \\
            \hline
        \end{tabular}
        \caption{Cumulated rewards and regret, for horizons $T=100$ and $T=10000$, \emph{averaged over $N=1000$ independent simulations}, for different algorithms.}
        \label{table:2:meanResults}
    \end{small}  % WARNING
\end{table}

\TODOL{Décrire les résultats !}
